---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# qhsR

<!-- badges: start -->
<!-- badges: end -->

The goal of qhsR is to provide a home for miscellaneous R functions that are useful to the CCF QHS department but do not warrant a standalone package.

## Installation

You can install the development version of qhsR from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("ClevelandClinicQHS/qhsR")
```

Details of the included functionality follow.

---

## CCF color palette

The `ccf_color_palette` functions provides users with easy access to CCF brand colors for use in plotting with `ggplot2` or base R plotting.

The code behind this color palette is largely based on the code from the Wes Anderson color palettes for R: [https://github.com/karthik/wesanderson](https://github.com/karthik/wesanderson) and a previous brand color palette I created at Memorial Sloan Kettering Cancer Center.

```{r}
library(ggplot2)
library(qhsR)
```

### The colors

Details about the CCF brand colors can be found at the [OnBrand website](https://onbrand.clevelandclinic.org/get-the-basics/#color-palette).

On a basic level, the CCF brand colors are stored as named values. You can see a complete list:

```{r}
ccf_cols()
```

You can access the hex color for a specific color:

```{r}
ccf_cols("ccf_green")
```

You can access the hex color for multiple colors:

```{r}
ccf_cols("ccf_blue", "ccf_green")
```


### Palettes

There are seven color palettes available. Note that these color palettes focus on using the CCF brand colors, and not on being color-blind friendly. Color combinations should be tested for color-blind accessibility as needed.

You can view a list of the color names and hex codes for a specific color palette:

```{r}
ccf_palettes[["main"]]
```

And you can also view the colors in a plot window.

#### main

The `main` color palette is based on the primary and secondary CCF brand colors.

```{r fig.height = 1}
ccf_palette("main")
```

#### bright

The `bright` color palette is based on the bright supplemental CCF brand colors.

```{r fig.height = 1}
ccf_palette("bright")
```

#### contrast

The `contrast` color palette mixes colors from `main` and `bright` in an order that should allow some distinction when plotting.

```{r fig.height = 1}
ccf_palette("contrast")
```

#### neutral

The `neutral` color palette is based on the neutral supplemental CCF brand colors.

```{r fig.height = 1}
ccf_palette("neutral")
```

#### all

The `all` color palette contains all colors from main, bright, and neutral for when a large number of colors are needed.

```{r fig.height = 1}
ccf_palette("all")
```

#### blues

The `blues` color palette only contains two colors and is meant to be used for continuous color scales where interpolation will be done between the high and low color.

```{r fig.height = 1}
ccf_palette("blues")
```

#### greens

Similarly, the `greens` color palette only contains two colors and is meant to be used for continuous color scales where interpolation will be done between the high and low color.

```{r fig.height = 1}
ccf_palette("greens")
```


### Plotting

Functionality is available to plot single or multiple colors, discrete color scales, and continuous color scales.

To use a single specific color, simply reference it by name.

```{r}
ggplot(mtcars, aes(x = hp, y = mpg)) +
  geom_point(size = 4, color = ccf_cols("ccf_green"))
```

You can do the same to use multiple specific colors by name using `scale_color_manual`.

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_manual(
    values = ccf_cols(c("ccf_green", "seagull", "maroon_flush"))
    )
```

To use the palettes, specify a palette by name as the `values` argument to `scale_color_manual` or `scale_fill_manual`. 

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_manual(values = ccf_palette("main"))
```

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_manual(values = ccf_palette("contrast"))
```

You can also pick and choose which colors you want by position in the palette.

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) +
  scale_color_manual(values = ccf_palette("main")[c(1, 4, 2)])
```

The `scale_color_gradientn` function can be used to add colors on a continuous scale, by adding the option `type = "continuous"` to `ccf_palette()`. Interpolation between colors in the palette will be done to create a continuous scale, and this is intended for use with the `blues` and `greens` palettes.

```{r}
ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Petal.Length)) +
  geom_point(size = 4) +
  scale_color_gradientn(colors = ccf_palette("greens", type = "continuous"))
```

### Setting the default color palette

You can set a default color palette for all plotting with {ggplot2} in a session using `set_ccf_palette()`. By default it will set the palette to "all", but any of the palettes can be selected, or specific colors can be specified. This will add custom versions of `scale_color_discrete` and `scale_fill_disrete` to the global environment, and will impact all following plotting that use color or fill.

```{r}
set_ccf_palette("contrast")

ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) +
  geom_point(size = 4) 
```

---











